### 2021-04-19 README.Rmd
rstudio, make

When the time comes, you can install this on CRAN.

@@

Right now, this package in development and is not available on CRAN. You can install the development version of `steveproj` from Github via the `devtools` package. I suppose using the `remotes` package would work as well.

@@

>>>>

When the time comes, you can install this on CRAN. Any version of this package on CRAN should be understood as a "stable" release that may lag behind the "development" versions available on Github. However, releases on CRAN should come with more confidence about quality control.

@@

A developmental version version of `{steveproj}` is available on Github and you can install it via the `{devtools}` package. I suppose using the `{remotes}` package would work as well.

@@

### A Comment on Make and Rstudio

The functions in this package work as intended in an R console, but this package realizes its full potential and its core functions are fully augmented through two additional pieces of software the user should already have installed. The first is [Rstudio](https://www.rstudio.com). Most dedicated R users are likely fully aware of Rstudio as an integrated desktop environment (IDE) and already have it installed and pre-configured to what they think is ideal for their workflow. I will only add that I think it advantageous for the sake of this package to adjust the pane layout such that the "source" pane is top left, the "console" pane is top right, the "environment" pane is bottom left, and the "files" pane is bottom right.

The second piece of software the user should install is [Make](https://en.wikipedia.org/wiki/Make_(software)). Make is a build automation tool built around a "Makefile", which contains a set of recipes that have various targets and dependencies. For each target, if the specified dependency is "newer" than the target (or if the target does not yet exist), the Makefile executes a command. Users will get a reproducible example of how this works, and they can learn by example from it, but it assumes the user already has it installed.

Installation of Make prior to installation of `{steveproj}` is not necessary; in fact, it's not even strictly necessary to have Make installed at all. It is, however, strongly encouraged. Linux users and Mac users should, in theory, have Make installed on their operating systems already (i.e. because both are UNIX-derivative and Make is a GNU program). Opening a terminal and entering the following command should confirm that.

```make
make -v
```

If the console output instead suggests Make is not installed, the user may want to search for how they can install it (given their particular flavor of Mac or Linux). For Mac users, most paths would lead to [installing or updating Xcode from the App Store](https://stackoverflow.com/questions/10265742/how-to-install-make-and-gcc-on-a-mac) through the popular [`Homebrew` package manager](https://brew.sh) should also do this. Ubuntu (Linux) users who, for some reason, don't already have this installed can install it via `sudo apt-get install build-essential` or `sudo apt-get -y install make` in a console.

Windows users will invariably have to install it since it will not come by default. [*The Carpentries* has a guide](https://swcarpentry.github.io/make-novice/setup) has a guide and installer to do this. Windows users may also want to [consider installing `Chocolately`](https://chocolatey.org), an apparent `Homebrew` analog for Windows users. Afterward, a simple `choco install make` command should work just fine.
